Supplemental material

### 2024-04-30 paper/supp_material.qmd
v1

Distribution of phase shift associated to the local parametrisation of the quadratic-linear (QL) filter using real time estimates of $\delta/\sigma$, by the bandwidth $h$ of the henderson filter used to estimate $\sigma$ and the degree $d$ of the trend to estimate $\delta$.
:::

@@

\justifying
*Note: nearest bandwidth moving average are used to estimate slope and concavity.*
*We thus do not distinguish local parametrisation and final local parametrisation which asumptions might not be plausible.*
*Indeed, using the same framework as for fixed bandwidth, the final local parametrisation for real time estimates would implie modelling a polynomial of degree 2 or 3 other 25 months (which doesn't seem plausible).*

>>>>

Distribution of phase shift associated to the local parametrisation of the quadratic-linear (QL) filter using real-time estimates of $\delta/\sigma$, by the bandwidth $h$ of the henderson filter used to estimate $\sigma$ and the degree $d$ of the trend to estimate $\delta$.
:::

@@

\justifying
*Note: nearest bandwidth moving average are used to estimate slope and concavity.*
*We thus do not distinguish local parametrisation and final local parametrisation which asumptions might not be plausible.*
*Indeed, using the same framework as for fixed bandwidth, the final local parametrisation for real-time estimates would implie modelling a polynomial of degree 2 or 3 other 25 months (which doesn't seem plausible).*
